{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
finisher for instantiation
translated single word

Now it is easy to define the control dependence region and the junction points for the source
language and deduce the ones for the assembly language from them. The first step is to label the
source language at the gefärdeten\todo{translate} regions with natural numbers:

@@

>>>>

Now it is easy to define the control dependence region and the junction points for the source
language and deduce the ones for the assembly language from them. The first step is to label the
source language at the regions at risk with natural numbers:

@@

The proof that this definition fulfills the properties from \nameref{sec:soundness} and all other
proofs can be found in the full version of the paper. \todo{cite the full version}

Now the instantiation of the framework is complete, except for the scheduler which was left undefined
in the paper.
